---
title: "STAT394 Group Project Report1 TEST"
author: "Ken MacIver, Tom Tribe, Jundi Yang, Mei Huang"
date: "`r Sys.Date()`"
classoption: 12pt
output: bookdown::pdf_document2
bibliography: ./Bibliography/MASTER.bib
header-includes: \usepackage{float}
                    \floatplacement{figure}{H}
                    \floatplacement{table}{H}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load ggplot and ggthemes

```{r, warning=FALSE, echo=FALSE, message=FALSE}
set.seed(198818350)
library(ggplot2)
require(ggplot2)
require(ggthemes)
library(ggstance)
```

# First Project Report TEST

## Introduction

We report on the dataset we have selected for our Group Project. It contains data on athletes from different sports. There are two categorical variables, 'Gender' and 'Sport', and seven continuous variables which are: weight, height, body mass index (BMI) etc, etc. 

## Platform and Data

The data comes from the website of the Australasian Data and Story Library (OzDASL) available at the following link http://www.statsci.org/data/oz/ais.txt, who have kindly allowed their data to be used for statistical teaching and learning purposes.

Categorical data:

* Sex = male or female
* Sport =  sport played

Numeric data:

*  Ht =  height in cm
*  Wt = weight in kg
*  LBM = lean body mass in kg
*  %Bfat = % body fat
*  BMI = body mass index (weight/height2)
*  RCC = red blood cell count
*  WCC = white blood cell count
*  Hc =  haematocrit
*  Hg  = haemoglobin
*  Ferr =  plasma ferritin concentration
*  SSF  = sum of skin folds

## Exploratory Data Analysis (EDA)

In this section we perform an exploratory analysis to see what sort of patterns emerge from the data.

Firstly, we load the data into R:

```{r}
# read data into R and display the first ten columns
# use relative file path to allow other users to load the dataset
sports <- read.csv("./Sports_data2.csv")

sports[1:10,]


```

Display scatterplots of all the variables against each other.

```{r}
plot(sports)
```

## Testing 
